DRAFT

### 2022-11-03 Draft.Rmd
Update Draft.Rmd

### • Trueprice
### 99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
```{r echo=FALSE, message=FALSE}
ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Price', y='Count') + xlim(0, 1200) 
```

@@

### Winter and spring are fully presented in the dataset, whereas there are no records for July, August, September, and October.
```{r echo=FALSE}
kable(count(df2, month)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### • Plot for classes
```{r echo=FALSE, message=FALSE}
datasummary(trueprice*class ~ Mean, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```
```{r echo=FALSE, message=FALSE}
ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 
  geom_bar(stat = 'summary') + labs(x='Class', y='Price for 1 night (in EUR)', fill = 'Class')
```

>>>>

### • Trueprice
### 99% of the prices are below 600 EUR, thus, the limit for x-axis in histogram was set to this value.
### The distribution of the prices is skewed to the right, therefore, we can conclude that the mean price is greater then the mode.
```{r echo=FALSE, message=FALSE}
ggplot(data=df2, aes(x=trueprice)) + geom_histogram(fill='navyblue', color='white') + 
  labs(x='Price fpr one night (in EUR)', y='Count') + xlim(0, 600) 
```

@@

### Winter and spring are fully presented in the dataset, whereas there are no records for July, August, September, and October.

```{r echo=FALSE}
kable(count(df2, month)) %>%
  kableExtra::kable_styling(position = "center", latex_options = "hold_position")
```

@@

### • Plot for classes
```{r echo=FALSE}
datasummary(trueprice*class ~ Mean, data = df2) %>%
   kableExtra::kable_styling(latex_options = "hold_position")
```
```{r echo=FALSE, message=FALSE}
ggplot(data = df2, aes(x=reorder(class, +trueprice), y=trueprice, fill = class)) + 
  geom_bar(stat = 'summary') + labs(x='Class', y='Price for 1 night (in EUR)', fill = 'Class')
```
